SSwAB-IT Phase 1 Analysis

### 2024-11-19 Jordana Hoppe/Home Collection/manuscript.qmd
plot updates for Jordana

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(likert)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning, include=FALSE}
# Use REDCap import
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_data.r"))
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_surveys.r"))
# Exclude missing subjects
data_exclude <- c("009-07", "009-17", "009-25", "009-37")
survey_exclude <- c(15, 27, 30, 34, 47)
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
survey_labels <- label(survey_data)[which(label(survey_data) != "")]
survey_labels[paste0(names(survey_labels), ".factor")] <- as.character(survey_labels)
labels <- c(labels, survey_labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Find tests with no growth
data$clinic_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("clinic_cx_results___\\d$", names(r))]), na.rm = T)
})
data$clinic_cx_no_growth.factor <- factor(data$clinic_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$res_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("res_cx_results___\\d$", names(r))]), na.rm = T)
})
data$res_cx_no_growth.factor <- factor(data$res_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$home_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("home_cx_results___\\d$", names(r))]), na.rm = T)
})
data$home_cx_no_growth.factor <- factor(data$home_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
# Genotype format
data$Genotype <- paste0(
  data$mutation1.factor == "F508del", "/", data$mutation2.factor == "F508del"
)
data$Genotype <- factor(data$Genotype,
  levels = c("TRUE/TRUE", "TRUE/FALSE", "FALSE/FALSE"),
  labels = c("F508del/F508del", "F508del/Other", "Other/Other")
)
```

@@

```{r}
agreement <- function(result_pattern, df = data) {
  cols <- paste0(
    c("clinic_cx_", "res_cx_", "home_cx_"),
    paste0(result_pattern, ".factor")
  )
  d <- df[, cols]
  colnames(d) <- c("Immediate", "Delayed", "Home")
  d <- d %>%
    mutate(across(everything(), ~ as.character(.)))
  d[d == "NA"] <- NA
  d[d == "Unchecked"] <- "Absent"
  d[d == "Checked"] <- "Present"
  fk <- kappam.fleiss(d)
  cat("\n")
  cat("### Agreement between all three methods")
  cat("\n")
  cat("\n")
  cat("#### Fleiss' kappa")
  cat("\n")
  cat("\n")
  f <- ftable(d)
  f %>%
    as.data.frame(.) %>%
    kable(.) %>%
    kable_styling(., "striped") %>%
    print(.)
  cat("\n")
  cat("\n")
  cat(
    "Overall Fleiss' kappa for the three tests was", round(fk$value, 3),
    paste0("(p = ", format.pval(fk$p.value, digits = 3, eps = 0.001), ")")
  )
  cat("\n")
  cat("\n")
  cat("#### Euler diagram")
  cat("\n")
  d %>%
    mutate(across(everything(), ~ as.numeric(. == "Present" | . == "No Growth"))) %>%
    drop_na(.) %>%
    euler(.) %>%
    plot(., quantities = T) %>%
    print(.)
  cat("\n")
  cat("\n")
  cat("### Pairwise agreement")
  cat("\n")
  d <- data.frame(lapply(d, factor, levels = c("Absent", "Present")))
  cat("\n")
  cat("#### Immediate vs. delayed (immediate as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Delayed"]),
    reference = d[, "Immediate"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("#### Immediate vs. home (immediate as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Home"]),
    reference = d[, "Immediate"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("#### Home vs. delayed (delayed as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Home"]),
    reference = d[, "Delayed"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
}
```

>>>>

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(likert)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning, include=FALSE}
# Use REDCap import
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_data.r"))
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_surveys.r"))
# Exclude missing subjects
data_exclude <- c("009-07", "009-17", "009-25", "009-37")
survey_exclude <- c(15, 27, 30, 34, 47)
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
survey_labels <- label(survey_data)[which(label(survey_data) != "")]
survey_labels[paste0(names(survey_labels), ".factor")] <- as.character(survey_labels)
labels <- c(labels, survey_labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Find tests with no growth
data$clinic_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("clinic_cx_results___\\d$", names(r))]), na.rm = T)
})
data$clinic_cx_no_growth.factor <- factor(data$clinic_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$res_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("res_cx_results___\\d$", names(r))]), na.rm = T)
})
data$res_cx_no_growth.factor <- factor(data$res_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$home_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("home_cx_results___\\d$", names(r))]), na.rm = T)
})
data$home_cx_no_growth.factor <- factor(data$home_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
labels <- as.list(labels)
# Genotype format
data$Genotype <- paste0(
  data$mutation1.factor == "F508del", "/", data$mutation2.factor == "F508del"
)
data$Genotype <- factor(data$Genotype,
  levels = c("TRUE/TRUE", "TRUE/FALSE", "FALSE/FALSE"),
  labels = c("F508del/F508del", "F508del/Other", "Other/Other")
)
```

@@

```{r}
agreement <- function(result_pattern, df = data) {
  cols <- paste0(
    c("clinic_cx_", "res_cx_", "home_cx_"),
    paste0(result_pattern, ".factor")
  )
  d <- df[, cols]
  colnames(d) <- c("Immediate", "Delayed", "Home")
  d <- d %>%
    mutate(across(everything(), ~ as.character(.)))
  d[d == "NA"] <- NA
  d[d == "Unchecked"] <- "Absent"
  d[d == "Checked"] <- "Present"
  fk <- kappam.fleiss(d)
  cat("\n")
  cat("### Agreement between all three methods")
  cat("\n")
  cat("\n")
  cat("#### Fleiss' kappa")
  cat("\n")
  cat("\n")
  f <- ftable(d)
  f %>%
    as.data.frame(.) %>%
    kable(.) %>%
    kable_styling(., "striped") %>%
    print(.)
  cat("\n")
  cat("\n")
  cat(
    "Overall Fleiss' kappa for the three tests was", round(fk$value, 3),
    paste0("(p = ", format.pval(fk$p.value, digits = 3, eps = 0.001), ")")
  )
  cat("\n")
  cat("\n")
  cat("#### Euler diagram")
  cat("\n")
  d %>%
    mutate(across(
      everything(),
      ~ as.numeric(. == "Present" | . == "No Growth")
    )) %>%
    drop_na(.) %>%
    venn(.) %>%
    plot(., quantities = T) %>%
    print(.)
  cat("\n")
  cat("\n")
  cat("#### Bar plot")
  cat("\n")
  cat("\n")
  # Format data
  bar_plot_df <- d %>%
    rowwise() %>%
    mutate(
      "Immediate vs. Delayed" = case_when(
        Immediate == "Present" & Delayed == "Present" ~ "Both Present",
        Immediate == "Absent" & Delayed == "Absent" ~ "Both Absent",
        .default = "Disagreed"
      ),
      "Immediate vs. Home" = case_when(
        Immediate == "Present" & Home == "Present" ~ "Both Present",
        Immediate == "Absent" & Home == "Absent" ~ "Both Absent",
        .default = "Disagreed"
      ),
      "Delayed vs. Home" = case_when(
        Delayed == "Present" & Home == "Present" ~ "Both Present",
        Delayed == "Absent" & Home == "Absent" ~ "Both Absent",
        .default = "Disagreed"
      ),
    ) %>%
    select(-c(Immediate:Home)) %>%
    pivot_longer(cols = `Immediate vs. Delayed`:`Delayed vs. Home`) %>%
    group_by(name) %>%
    count(value) %>%
    mutate(pct = (n / sum(n)) * 100)
  # Plot
  p = ggplot(bar_plot_df, aes(x = name, fill = value, y = n)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste0(sprintf("%1.1f", pct), "%")),
      position = position_stack(vjust = 0.5)
    ) +
    ylab("Samples (N)") +
    theme_classic() +
    theme(legend.title = element_blank(), axis.title.x = element_blank())
  cat("\n")
  cat("\n")
  show(p)
  cat("\n")
  cat("\n")
  cat("### Pairwise agreement")
  cat("\n")
  d <- data.frame(lapply(d, factor, levels = c("Absent", "Present")))
  cat("\n")
  cat("#### Immediate vs. delayed (immediate as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Delayed"]),
    reference = d[, "Immediate"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("#### Immediate vs. home (immediate as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Home"]),
    reference = d[, "Immediate"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("#### Home vs. delayed (delayed as reference)")
  cat("\n")
  cat("\n")
  cat("##### Confusion matrix")
  cat("\n")
  cat("\n")
  c <- confusionMatrix((d[, "Home"]),
    reference = d[, "Delayed"], positive = "Present", mode = "everything"
  )
  print(kable(c$table, digits = 3))
  cat("\n")
  cat("\n")
  cat("##### Agreement")
  cat("\n")
  cat("\n")
  print(kable(c$overall, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
  cat("##### Sensitivity, specificity, etc.")
  cat("\n")
  cat("\n")
  print(kable(c$byClass, digits = 3, col.names = NULL))
  cat("\n")
  cat("\n")
}
```

### 2024-11-19 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
plot updates for Jordana

```{r data cleaning}
#| include: false
# Import from REDCap
unlockREDCap(c(rcon = "SSwAB-IT (New)"),
  keyring = "API_KEYs",
  envir = 1,
  url = "https://redcap.ucdenver.edu/api/"
)
exportBulkRecords(list(db = rcon), envir = 1)
# Exclude
exclude <- c("01-030_W", "01-038_W", "02-0038", "02-0039", "04-001")
# Combine collection results
df <- full_join(db_cos_collection_results, db_sos_collection_results)
# Add dates to demographics
db_demographics <- left_join(db_demographics,
  df %>% select(record_id, cos_result_date),
  by = join_by(record_id)
)
db_demographics$age_at_cos <- as.numeric(difftime(db_demographics$cos_result_date,
  db_demographics$dob,
  units = "days"
)) / 365.25
db_demographics$age_group <- cut(db_demographics$age_at_cos,
  c(-Inf, 10, 18, 30, Inf),
  right = F
)
# Format
df <- df %>%
  select(
    record_id,
    staphylococcus_aureus_cos:other_result_cos,
    staphylococcus_aureus_sos:other_result_sos
  ) %>%
  filter(!record_id %in% exclude)
# Remove empty demographics rows
db_demographics <- db_demographics %>%
  filter(
    redcap_event_name == "Clinic Visit (Arm 1: Eligible)",
    !record_id %in% exclude
  )
# Excluded participants
db_medications <- db_medications %>% filter(!record_id %in% exclude)
# Combine race and ethnicity columns
races <- c(
  "American Indian or Alaskan Native", "Asian", "Hawaiian or Pacific Islander",
  "Black or African American", "White", "Unknown", "Other"
)
ethnicities <- c("Hispanic", "Non-Hispanic", "Unknown/Not Reported")
db_demographics$Race <- apply(db_demographics, 1, function(r) {
  w <- which(r[grep("race", names(r))] == "Checked")
  if (length(w) == 1) {
    return(races[w])
  } else if (length(w) > 1) {
    return("Multiple Races")
  } else if (length(w) == 0) {
    return(NA)
  }
})
db_demographics$Ethnicity <- apply(db_demographics, 1, function(r) {
  w <- which(r[grep("ethnicity", names(r))] == "Checked")
  if (length(w) == 1) {
    return(ethnicities[w])
  } else if (length(w) > 1) {
    return(paste(ethnicities[w], sep = "/"))
  } else if (length(w) == 0) {
    return(NA)
  }
})
# Add groups to other dataframes
db_medications <- left_join(db_medications,
  db_demographics %>% select(record_id, group),
  by = join_by(record_id)
)
# Bug list
bugs <- c(
  "staphylococcus_aureus", "haemophilus_influenza", "pseudomonas_aeruginosa",
  "pseudomonas_non_aero", "s_maltophilia", "burkholderia", "aspergillus", "ntm",
  "other"
)
bug_names <- c(
  "S. aureus", "H. influenza", "P. aeruginosa", "Pseudomonas non-aeruginosa",
  "S. maltophilia", "Burkholderia", "Aspergillus", "NTM", "Other"
)
# Convert yes/no to positive/negative
df[, paste0(bugs, "_cos")] <- lapply(df[, paste0(bugs, "_cos")], factor,
  levels = c("No", "Yes"), labels = c("Negative", "Positive")
)
df[, paste0(bugs, "_sos")] <- lapply(df[, paste0(bugs, "_sos")], factor,
  levels = c("No", "Yes"), labels = c("Negative", "Positive")
)
# Create overall columns (any bug detected in sample)
df$overall_cos <- apply(df, 1, function(r) {
  any(r[paste0(bugs, "_cos")] == "Positive")
})
df$overall_cos <- factor(df$overall_cos,
  levels = c(F, T), labels = c("Negative", "Positive")
)
df$overall_sos <- apply(df, 1, function(r) {
  any(r[paste0(bugs, "_sos")] == "Positive")
})
df$overall_sos <- factor(df$overall_sos,
  levels = c(F, T), labels = c("Negative", "Positive")
)
# Add overall to list
bugs <- c("overall", bugs)
bug_names <- c("Across all bugs", bug_names)
bug_list <- as.list(bug_names)
names(bug_list) <- bugs
# Add groups to dataframe
df <- left_join(df, db_demographics %>% select(record_id, group, age_group),
  by = join_by(record_id)
)
df <- left_join(df, db_medications, by = join_by(record_id, group))
# Feasibility
db_feasibility <- db_feasibility %>% filter(!record_id %in% exclude)
```

@@

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  print(plot(euler(d == "Negative"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5"))
  ))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  print(plot(euler(d == "Positive"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5"))
  ))
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  # Print
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, label = list(
      agree ~ "Agree (Both Positive/Positive and Negative/Negative)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e6)) %>%
    separate_p_footnotes() %>%
    print()
  cat("\n")
}
```

>>>>

```{r data cleaning}
#| include: false
# Import from REDCap
unlockREDCap(c(rcon = "SSwAB-IT (New)"),
  keyring = "API_KEYs",
  envir = 1,
  url = "https://redcap.ucdenver.edu/api/"
)
exportBulkRecords(list(db = rcon), envir = 1)
# Exclude
exclude <- c("01-030_W", "01-038_W", "02-0038", "02-0039", "04-001")
# Combine collection results
df <- full_join(db_cos_collection_results, db_sos_collection_results)
# Add dates to demographics
db_demographics <- left_join(db_demographics,
  df %>% select(record_id, cos_result_date),
  by = join_by(record_id)
)
db_demographics$age_at_cos <- as.numeric(difftime(db_demographics$cos_result_date,
  db_demographics$dob,
  units = "days"
)) / 365.25
db_demographics$age_group <- cut(db_demographics$age_at_cos,
  c(-Inf, 10, 18, 30, Inf),
  right = F
)
# Format
df <- df %>%
  select(
    record_id,
    staphylococcus_aureus_cos:other_result_cos,
    staphylococcus_aureus_sos:other_result_sos
  ) %>%
  filter(!record_id %in% exclude)
# Remove empty demographics rows
db_demographics <- db_demographics %>%
  filter(
    redcap_event_name == "Clinic Visit (Arm 1: Eligible)",
    !record_id %in% exclude
  )
# Excluded participants
db_medications <- db_medications %>% filter(!record_id %in% exclude)
# Combine race and ethnicity columns
races <- c(
  "American Indian or Alaskan Native", "Asian", "Hawaiian or Pacific Islander",
  "Black or African American", "White", "Unknown", "Other"
)
ethnicities <- c("Hispanic", "Non-Hispanic", "Unknown/Not Reported")
db_demographics$Race <- apply(db_demographics, 1, function(r) {
  w <- which(r[grep("race", names(r))] == "Checked")
  if (length(w) == 1) {
    return(races[w])
  } else if (length(w) > 1) {
    return("Multiple Races")
  } else if (length(w) == 0) {
    return(NA)
  }
})
db_demographics$Race <- factor(db_demographics$Race,
  levels = c(
    "White", "Other", "Multiple Races", "American Indian or Alaskan Native"
  )
)
db_demographics$Ethnicity <- apply(db_demographics, 1, function(r) {
  w <- which(r[grep("ethnicity", names(r))] == "Checked")
  if (length(w) == 1) {
    return(ethnicities[w])
  } else if (length(w) > 1) {
    return(paste(ethnicities[w], sep = "/"))
  } else if (length(w) == 0) {
    return(NA)
  }
})
db_demographics$Ethnicity <- factor(db_demographics$Ethnicity,
  levels = c("Non-Hispanic", "Hispanic", "Unknown/Not Reported")
)
# Drop empty levels
db_demographics <- droplevels(db_demographics)
# Add groups to other dataframes
db_medications <- left_join(db_medications,
  db_demographics %>% select(record_id, group),
  by = join_by(record_id)
)
# Bug list
bugs <- c(
  "staphylococcus_aureus", "haemophilus_influenza", "pseudomonas_aeruginosa",
  "pseudomonas_non_aero", "s_maltophilia", "burkholderia", "aspergillus", "ntm",
  "other"
)
bug_names <- c(
  "S. aureus", "H. influenza", "P. aeruginosa", "Pseudomonas non-aeruginosa",
  "S. maltophilia", "Burkholderia", "Aspergillus", "NTM", "Other"
)
# Convert yes/no to positive/negative
df[, paste0(bugs, "_cos")] <- lapply(df[, paste0(bugs, "_cos")], factor,
  levels = c("No", "Yes"), labels = c("Negative", "Positive")
)
df[, paste0(bugs, "_sos")] <- lapply(df[, paste0(bugs, "_sos")], factor,
  levels = c("No", "Yes"), labels = c("Negative", "Positive")
)
# Create overall columns (any bug detected in sample)
df$overall_cos <- apply(df, 1, function(r) {
  any(r[paste0(bugs, "_cos")] == "Positive")
})
df$overall_cos <- factor(df$overall_cos,
  levels = c(F, T), labels = c("Negative", "Positive")
)
df$overall_sos <- apply(df, 1, function(r) {
  any(r[paste0(bugs, "_sos")] == "Positive")
})
df$overall_sos <- factor(df$overall_sos,
  levels = c(F, T), labels = c("Negative", "Positive")
)
# Add overall to list
bugs <- c("overall", bugs)
bug_names <- c("Across all bugs", bug_names)
bug_list <- as.list(bug_names)
names(bug_list) <- bugs
# Add groups to dataframe
df <- left_join(df, db_demographics %>% select(record_id, group, age_group),
  by = join_by(record_id)
)
df <- left_join(df, db_medications, by = join_by(record_id, group))
# Feasibility
db_feasibility <- db_feasibility %>% filter(!record_id %in% exclude)
```

@@

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  print(plot(euler(d == "Negative"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  print(plot(euler(d == "Positive"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  # Print
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, label = list(
      agree ~ "Agree (Both Positive/Positive and Negative/Negative)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e6)) %>%
    separate_p_footnotes() %>%
    print()
  cat("\n")
}
```
